Modelling the emergence of whisker barrels

### 2020-05-27 paper/briefpaper/brief.tex
Wednesday work on figures

The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
% EITHER
%%redefined
%%%
%%\begin{equation} \label{eq:comp}
%%\color{blue}
%%\chi_i(\mb{x}, t) = \frac{\bar{a}_i F}{N-1} \nabla \sum_{j\ne i}{a_j}
%%\color{black}
%%\end{equation}
% OR
\cmnt{first define a quantity to represent the branching density of all
  \emph{other} TC types; $\hat{a}_i = \sum_{j\ne i}{a_j}$; then set the term
  $\chi_i$ to be}
%
\begin{equation} \label{eq:comp}
\color{blue}
\chi_i(\mb{x}, t) = \frac{a_i F}{N-1} \nabla \hat{a}_i,
\color{black}
\end{equation}
%
\cmnt{which contributes to the \emph{flux of axonal branching} by making
  branching density for each projection `flow away' from regions} where the
branches of other projections are dense. \cmnt{$F$ parameterizes the strength
  of this competitive interaction.} Note that this operation is local to
individual afferent projections.

@@

@@

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) at each location the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii) the branch density of each projection is
conserved over time (Eq.\,\ref{eq:norm}).

>>>>

The term in parentheses in Eq.\,\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
redefined
%
\begin{equation} \label{eq:comp}
\color{blue}
\chi_i(\mb{x}, t) = \frac{\epsilon a_i}{N-1} \nabla \textstyle\sum_{j\ne i}{a_j}
\color{black}
\end{equation}
%
\cmnt{which contributes to the \emph{flux of axonal branching} as an
  additional diffusion-like term which makes the branching density for a given
  projection `flow away' from regions} where the branches of other projections
become dense. \cmnt{$\epsilon$ parameterizes the strength of this competitive
  interaction.} Note that this operation is local to individual afferent
projections.

@@

\begin{figure}
\begin{fullwidth}
\includegraphics[width=\linewidth]{./paramsweep.png}
\caption{\cmnt{\textbf{A} Parameter sweep caption goes here}}
\label{fig:paramsweep}
\end{fullwidth}
\end{figure}

\cmnt{Parameter sweep paragraph goes here.}

@@

The present results suggest that the key requirements for the emergence of
realistic barrel patterning are i) at each cortical location thalamocortical
projections compete for a limited number of available synaptic connections
(Eqs.~\ref{eq:dc}--\ref{eq:da}), ii) \cmnt{review} at each location the branching rate of a
given projection is reduced by the density of other projections
(Eq.\,\ref{eq:comp}), and iii)  \cmnt{review} the branch density of each projection is
conserved over time (Eq.\,\ref{eq:norm}).
